---
title: "banqueHydro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{banqueHydro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(banqueHydro)
```


The two main functions of package `banqueHydro` are:

- `bh_get_qtvar()` (collects measures of discharge at varying time intervals)
- `bh_get_qjm()` (collects mean daily discharge)

Their main arguments correspond to **station code** and **starting (t1) and ending (t2) dates**.

The **station codes** can be explored [here](http://www.hydro.eaufrance.fr/selection.php?consulte=rechercher).

For **QTVAR** (measures at varying time intervals), t1 and t2 correspond to date-time formatted as "dd/MM/year HH:mm":

```{r}
df_qtvar <- bh_get_qtvar(station="V2942010",
                         t1="05/02/2007 15:00",
                         t2="08/04/2007 18:00")

df_qtvar[1:10,]
```


For **QJM** (mean daily measures), t1 and t2 correspond to starting and ending years:

```{r}
df_qjm <- bh_get_qjm(station="V2942010",
                     t1=2008,
                     t2=2010)
df_qjm[1:10,]
```

Please be aware that web-scraping is a **resource-consuming process** and that one should refrain from submitting very demanding or unnecessary/redundant queries. The functions of package `banqueHydro` include by default delays to ensure that the queries do not overload the banqueHydro servers. Due to these safeguards, the completion of the requests above can take quite a long time (a few minutes for each of the commands above). Hence, you should **make sure to save the results of these queries** as R objects first, and then **as local files**, for instance through:

```{r,eval=FALSE}
saveRDS(df_qtvar,"df_qtvar.RDS")
saveRDS(df_qjm,"df_qjm.RDS")
```

The tables are then saved as R data structures which you can later read with:

```{r,eval=FALSE}
readRDS("df_qtvar.RDS")
readRDS("df_qjm.RDS")
```


